Overview

### 2021-12-07 README.Rmd
Bump version; update NEWS; ready for CRAN
Replace png logo with svg logo

# oolong <img src="man/figures/oolong_logo.png" align="right" height="200" />

@@

Please refer to the [overview](overview_gh.md) for an introduction to this package. If you need to deeploy the test online, please refer to the [Deployment Vignette](deploy_gh.md). If you use BTM, please refer to the [BTM Vignette](btm_gh.md).

>>>>

# oolong <img src="man/figures/oolong_logo.svg" align="right" height="200" />

@@

Please refer to the [overview](overview_gh.md) for an introduction to this package. If you need to deploy the test online, please refer to the [Deployment Vignette](deploy_gh.md). If you use BTM, please refer to the [BTM Vignette](btm_gh.md).
